The transition redshift as a probe of reionization

### 2019-08-12 paper/ms.tex
Add def of transition redshift

@@

@@

\section{Methods} \label{sec:methods}
\subsection{21cmFAST} \label{ssec:tfast}
We generate realizations of the 21~cm field for our different EoR models using
the publicly available code \tfast{}
v1.3\footnote{\url{https://github.com/andreimesinger/21cmFAST}, commit:
\texttt{42e7566}}. Spin temperature fluctuations are computed and the
excursion set approach is used to identify the ionized regions
\citep{2011MNRAS.411..955M}. Rather than using the mean collapsed fraction, we
use the halo field to compute the ionization and 21~cm fields, since we are
interested in the evolution at early redshifts where the Poisson statistics of
the halo field can be important.

>>>>

\newcommand{\hoverMpc}{\ensuremath{h\,\text{Mpc}^{-1}}}

@@

\newcommand{\zst}{\ensuremath{z_{\star}}}

@@

\section{Methods} \label{sec:methods}
\subsection{The transition redshift} \label{ssec:ztran_def}
The transition redshift $\zst(k)$ is defined by a field $x$ which traces the
density field on large scales and the condition that
\beq \label{eq:ztran_def}
P_{21,x}(k, \zst(k)) \equiv 0\text{.}
\eeq
If more than one such \zst{} exists, then we choose the lowest one where
$P_{21,x}$ last transitioned from positive to negative.

\subsection{21cmFAST} \label{ssec:tfast}
We generate realizations of the 21~cm field for our different EoR models using
the publicly available code \tfast{}
v1.3\footnote{\url{https://github.com/andreimesinger/21cmFAST}, commit:
\texttt{42e7566}}. Spin temperature fluctuations are computed and the
excursion set approach is used to identify the ionized regions
\citep{2011MNRAS.411..955M}. Rather than using the mean collapsed fraction, we
use the halo field to compute the ionization and 21~cm fields, since we are
interested in the evolution at early redshifts where the Poisson statistics of
the halo field can be important.
